Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-19 2_SSL_EES/article/article_main.tex
added figures to results section

\subsection{Device Performance Metrics}

@@

\subsubsection{Conversion Efficiency $\eta_{CE}$}

@@

>>>>

\subsection{Device Performance Metrics}
\label{sec:device_performance_metrics}

@@

\subsubsection{Conversion Efficiency $\eta_{C}$}

@@

\subsection{Performance Metrics Calculations}

The contribution of individual technology innovations and spillovers to the progress in the overall device efficiency over time is estimated by the index decomposition analysis, which is commonly used in energy economics \cite{Ang2019}. Specifically, we use the additive logarithmic mean Divisia index method I (LMDI-I), also known as the Additive Sato-Vartia indicator \cite{deBoer2019}. It was developed by Boyd in 1987 \cite{Boyd1987} on the basis of Divisia index, a method in statistical economics \cite{Diewert1988}, and subsequently refined \cite{Ang1997}.

\section{Results}

\begin{figure*}[h!]
 \centering
 \includegraphics[width=16.5cm]{2_SSL_EES/article/figures/waterfall_performance_2003.pdf}
 \includegraphics[width=16.5cm]{2_SSL_EES/article/figures/waterfall_performance_2010.pdf}
 \caption{Waterfall diagrams of the loss channels in a generic mid/high-power LED package for 2003 (top panel) and 2010 (bottom panel), normalized to 1 Watt of electric power input (yellow bar on the left). Sub-efficiencies corresponding to each loss channel are listed below each column and described in Section \ref{sec:device_performance_metrics}. Numbers for each loss channel indicate energy losses both in relative terms of input power (in percent) at the point of the channel and absolute values (in Watts). Percentages for red, green and blue loss channels indicate losses of remaining red/green/blue light energy. The following corresponding LED architectures from Figure \ref{fgr:chip_architecture_overview} are shown for reference: 2003 (top panel) – flip-chip with YGAG phosphor; 2010 (bottom panel) – flip-chip with 258 phosphor. Details on phosphors are provided in Table XX and SI section XX. Overall LED package efficiency is $\eta_L = 5.8\%$ in 2003 and $\eta_L = 12.6\%$ in 2010. Abbreviations: Scat. = Scattering. Source: own elaboration based on data from sources listed in SI, section XX.}
 \label{fgr:waterfall_1}
\end{figure*}
